---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# explosbuck

<!-- badges: start -->
<!-- badges: end -->

The goal of explosbuck is to explore the Starbucks coffeehouses data and compare the
coffeehouses in countries. 

https://etc5523-2022.github.io/rpkg-xxuu0086/

## Installation

You can install the development version of explosbuck from [GitHub](https://github.com/etc5523-2022/rpkg-xxuu0086) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-xxuu0086/explosbuck")
```

## Usage

```{r}
library(explosbuck)
```

## Examples
```{r}
library(knitr)
```


To access Starbucks data, for first six rows:

```{r}
head(starbucks) %>%
  kable()
```

To find two letter combination country code, for first six rows:

```{r}
head(ISOcode) %>%
  kable()
```

To count total number of Starbucks coffeehouses in Australia:

```{r}
# Use ISOcode to find the code for Australia is AU
# filter(ISOcode, Country == "Australia")
count_sbuck(code = "AU") %>%
  kable()
```

To see difference in total number of Starbucks coffeehouses between Australia and United States:

```{r}
diff_sbuck(code1 = "AU", code2 = "US") %>%
  kable()
```

A plot to compare the total number of coffeehouses for Australia, United States and Canada:

```{r out.width = "70%", out.height="70%", fig.align = 'center'}
plot_sbuck(code = c("AU", "US", "CA"))
```
