---
title: "Instructions for explosbuck package"
author: "Xianghe XU"
email: "xxuu0086@monash.student.edu"
department: "Department of Econometrics and Business Statistics"
footer: "Package : explosbuck"
format: 
  revealjs:
    transition: concave
    logo: Image/monash-university-vector-logo.png
    theme: league
    center: true
---

```{r setup, include = FALSE}
library(explosbuck)
library(tidyverse)
library(kableExtra)
library(knitr)

knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  message = FALSE, 
  warning = FALSE, 
  error = FALSE,  
  out.width = "70%",
  fig.width = 8, 
  fig.height = 6,
  fig.align = 'center',
  fig.retina = 3)
```

## Aim & Motivation

. . .

- Explore Starbucks data

. . .

- Calculate __Total__ and __Difference__ of coffeehouses

. . . 

- Compare number of coffeehouses between countries

## Installation

- How to install package explosbuck ?

. . . 

[https://github.com/etc5523-2022/rpkg-xxuu0086](https://github.com/etc5523-2022/rpkg-xxuu0086)

<br>

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-xxuu0086/explosbuck")
```

<br>

. . . 

<center> __Simple !__ <center>

. . . 

## Data & Function

. . . 

### Data

- __starbucks__

- ISOcode, tim_hortons, dunkin_donuts

. . . 

### Functions

- count_sbuck()

- diff_sbuck()

- plot_sbuck() (Shiny-parameterized function)

- run_app() (launch Shiny app)

. . . 

## Data : starbucks

- A data frame with 25600 rows and 13 variables.

```{r}
dim(starbucks) 
```

. . . 

- __Business related__ and __geographical__ information.

```{r}
names(starbucks) 
```

. . . 

## Data : ISOcode

- A two letter combination country code & country name 

- Complementary data to the use of functions


```{r}
head(ISOcode, 2) %>%
  kable() %>%
  kable_material()
```


## Function : count_sbuck()

- Count the total number of Starbucks coffeehouses.

```{r eval = FALSE}
count_sbuck(code)
```

<br>

. . . 

### Example :

```{r}
Australia <- filter(ISOcode, Country == "Australia")[1,1]
count_sbuck(code = Australia) %>%
  kable() 
```

. . . 

## Function : diff_sbuck()

- Calculate the difference in number of coffeehouses of two countries

```{r eval = FALSE}
diff_sbuck(code1, code2)
```

<br>

. . . 

### Example :

```{r}
Australia <- filter(ISOcode, Country == "Australia")[1,1]
China <- filter(ISOcode, Country == "China")[1,1]
diff_sbuck(code1 = Australia, code2 = China) 
```

. . . 

## Function : plot_sbuck()
- Shiny-parameterized function

- A plot to compare total coffeehouses in countries

```{r eval = FALSE}
plot_sbuck(code)
```

<br>



### Example :

```{r eval = FALSE}
Australia <- filter(ISOcode, Country == "Australia")[1,1]
China <- filter(ISOcode, Country == "China")[1,1]
Canada <- filter(ISOcode, Country == "Canada")[1,1]

plot_sbuck(code = c(Australia, China, Canada)) 
```

## Continue . .  

```{r eval = FALSE}
plot_sbuck(code = c(Australia, China, Canada)) 
```

. . . 

Alternatively

. . . 

```{r out.width = "60%"}
plot_sbuck(code = c("AU", "CN", "CA")) 
```

. . . 

## Continue . . 

Australia, China, Canada, 

. . . 

United States

. . . 

```{r out.width = "60%"}
plot_sbuck(code = c("AU", "CN", "CA", "US")) 
```

## Function : run_app()

- Launch Shiny app 

``` r 
run_app()
```

<br>

## More 

### Shiny app site :

- [https://kmmcvr-xianghe-xu.shinyapps.io/global-coffee-chain-xxuu0086/](https://kmmcvr-xianghe-xu.shinyapps.io/global-coffee-chain-xxuu0086/)

### Blog :

- [https://xxuu0086.quarto.pub/global-coffee-chain/](https://xxuu0086.quarto.pub/global-coffee-chain/)

# Thank you!
