---
title: "Guide to explosbuck"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Guide to explosbuck}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(explosbuck)
```

# Description

explosbuck is a package using for explore the Starbucks coffee chain data set, it also provides the calculation of the total and difference of number of coffeehouses for a particular country or countries. 

This package has 4 build-in data sets which are named as **starbucks**, **tim_hortons**, **dunkin_donuts** and **ISOcode**, and this package is mainly focused on data set **starbucks**. All data set are come from or derived from [tidytuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2018/2018-05-07/week6_coffee_chains.xlsx).

This vignette provides examples on how to use functions of package _explosbuck_ to perform: 

- Calculation of total number of Starbucks coffeehouses for a country.
- Calculation of difference in number of Starbucks coffeehouses between two countries.
- Visualization of total number of Starbucks coffeehouses in various countries.


## Example of the Package

```{r}
library(knitr)
```

### 1. count_sbuck

To count total number of Starbucks coffeehouses in Australia:

```{r}
# Use ISOcode to find the code for Australia is AU
# filter(ISOcode, Country == "Australia")
count_sbuck(code = "AU") %>%
  kable()
```

### 2. diff_sbuck

To see difference in total number of Starbucks coffeehouses between Australia and United States:

```{r}
diff_sbuck(code1 = "AU", code2 = "US") %>%
  kable()
```

### 3. plot_sbuck

A plot to compare the total number of coffeehouses for Australia, China and Canada:

```{r out.width = "70%", out.height="70%", fig.align = 'center'}
plot_sbuck(code = c("AU", "CN", "CA"))
```

